Observed vs. Simulated Year Comparison

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create capacity relationship figure

>>>>

```{r captions}
beta_caption = "
  Estimated relationship between parr capacity and weighted usable habitat length.
  Darker grey/thicker error bars represent 80% credible regions and lighter grey/thinner error bars represent 95% credible regions.
"

```

```{r beta-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(beta_caption), time_it = TRUE}
# extract posterior summaries of the capacity parameters
beta_ests = post_summ(post, "^beta[", probs = c(0.025, 0.1, 0.5, 0.9, 0.975))

# extract posterior samples of the slope parameter
beta_per = post_subset(post, "lambda", TRUE)

# create a sequence of WUL values to predict capacity at
wul_seq = seq(0, max(jags_data$wul) * 1.1, length = 30)

# obtain the regression line for each posterior sample
pred_beta = t(sapply(beta_per, function(slope) wul_seq * slope))

# summarize posterior of regression line
pred_beta_summ = apply(pred_beta, 2, function(x) c(mean = mean(x), quantile(x, c(0.025, 0.1, 0.5, 0.9, 0.975))))

# empty plot with correct labeling/dimensions
mypar(mfrow = c(1,1), col.axis = "black")
plot(1,1, type = "n", xlim = range(wul_seq),
     # ylim = c(0, max(beta_ests["97.5%",], pred_beta_summ["97.5%",])),
     ylim = c(0, 3000) * 1000,
     xlab = "",
     ylab = "", yaxt = "n")

# draw prettier y-axis
at_y = c(0, 1000, 2000, 3000) * 1000
axis(side = 2, at = at_y, labels = at_y/1000)
usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])

# draw the regression uncertainty
polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["2.5%",], rev(pred_beta_summ["97.5%",])), border = NA, col = tranp_col)
polygon(x = c(wul_seq, rev(wul_seq)), y = c(pred_beta_summ["10%",], rev(pred_beta_summ["90%",])), border = NA, col = tranp_col)

# draw the posterior mean regression line
lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)

# draw the population-specific capacity estimates w/error bars and labels
segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)

# draw the population labels
xoff = 0.015
yoff = 0.03
text(x = jags_data$wul      + xdiff * c(1.5,-1,1,1) * xoff,
     y = beta_ests["mean",] + ydiff * c(1,-1,1,1) * yoff,
     labels = c("CAT", "LOS", "MIN", "UGR"), pos = c(2,4,2,2), font = 1, cex = 0.8)

# add axis labels
axis_labels("Weighted Usable Habitat Length (km)", "Parr Capacity (Thousands)")
```
